Deployable Probabilistic Programming

### 2019-07-01 paper/paper.tex
removed copyright
vector elementals

Functions are considered elementals (and must have a
registered derivative) if their signature is of kind
\lstinline{func (float64, float64*) float64}; that is, 
one or more non-variadic \lstinline{float64} arguments and
\lstinline{float64} return value. For example, function
\lstinline{func (float64, float64, float64) float64}
is considered elemental, while functions
\begin{itemize}
  \item \lstinline{func (...float64) float64}
  \item \lstinline{func ([]float64) float64}
  \item \lstinline{func (int, float64) float64}
\end{itemize}
are not. Gradients for selected functions from the
\lstinline{math} package are pre-defined (\lstinline{Sqrt},
\lstinline{Exp}, \lstinline{Log}, \lstinline{Pow},
\lstinline{Sin}, \lstinline{Cos}, \lstinline{Tan}). Auxiliary
elemental functions with pre-defined gradients are provided in a
separate package.

>>>>

Functions are considered elementals (and must have a
registered derivative) if their signature is either of kind
\lstinline{func (float64, float64*) float64}, that is, 
one or more non-variadic \lstinline{float64} arguments and
\lstinline{float64} return value, or \lstinline{func([]float64) float64}.
For example, functions
\begin{itemize}
	\item \lstinline{func foo(float64, float64, float64) float64}
	\item \lstinline{func bar([]float64) float64}
\end{itemize}
are considered elemental, while functions
\begin{itemize}
  \item \lstinline{func fee(...float64) float64}
  \item \lstinline{func buz(int, float64) float64}
\end{itemize}
are not. Gradients for selected functions from the
\lstinline{math} package are pre-defined (\lstinline{Sqrt},
\lstinline{Exp}, \lstinline{Log}, \lstinline{Pow},
\lstinline{Sin}, \lstinline{Cos}, \lstinline{Tan}). Auxiliary
elemental functions with pre-defined gradients are provided in a
separate package.
